A pipeline to analyse time-course gene expression data

### 2021-02-05 scripts/manuscript.Rmd
More on supplementaries
pff…

keywords: >
    time-course gene expression data, clustering, differential expression,
    workflow
vignette: >
    %\VignetteIndexEntry{A worfklow for low-level analyses of scRNA-seq data}
    %\VignetteEngine{knitr::rmarkdown}
header-includes:
   - \usepackage{float}
output: pdf_document
bibliography: bibliography.bib
always_allow_html: yes
---

@@

```{r make_timepoints_contarts}
# Define contrasts	
contrasts = create_timepoints_contrasts(moanin_model,"M", "VL")
```

@@

```{r showMissingDEGenes, echo=FALSE, fig.cap="The expression values over time for 10 genes found significant DE in timepoints 48,60,120,168H, but not in the 72H timepoint."}
exampleGenes<-names(signifCombos[signifCombos=="48,60,120,168"][1:10])
plot_splines_data(moanin_model, subset_data=exampleGenes,
		  colors=ann_colors$Group, smooth=TRUE)
```

>>>>

keywords: >
    time-course gene expression data, clustering, differential expression,
    workflow
vignette: >
    %\VignetteIndexEntry{A worfklow for low-level analyses of scRNA-seq data}
    %\VignetteEngine{knitr::rmarkdown}
header-includes:
   - \usepackage{float}
output: word_document
bibliography: bibliography.bib
always_allow_html: yes
---

@@

```{r make_timepoints_contarts}
# Define contrasts	
contrasts = create_timepoints_contrasts(moanin_model, "M", "VL")
```

@@

```{r showMissingDEGenes, echo=FALSE, fig.width=10, fig.height=12, fig.cap="The expression values over time for 10 genes found significant DE in timepoints 48,60,120,168H, but not in the 72H timepoint."}
exampleGenes<-names(signifCombos[signifCombos=="48,60,120,168"][1:10])
plot_splines_data(moanin_model, subset_data=exampleGenes,
		  colors=ann_colors$Group, smooth=TRUE)
```
